link the shotgun fid and the actual sample and outcome table

### 2020-11-24 scripts/38_link_shotgun_fid_with_pheno.Rmd
yeah finally did this .... and now AG can help me upload

@@

```{r}

df %>% 
  write_csv('/Volumes/vandenbrinklab/Angel_Dai/Full_human_shotgun_catalog/shotgun_italy_earlier.csv')
```

@@

```{r}

@@

```{r}
source('../../../microbiome_db/SQL/scripts/upload_data_from_query_OTU_AD.R')
upload_data_from_query_OTU(1) # changed the file path of the table getting uploaded 
```

>>>>

italy_all %>% 
  write_csv('../data/shotgun_pheno/italy_all_earlier.csv')

@@

@@

```{r}
# get the file path of the shotgun files 
upenn <- c('Project_11341')
upenn2 <- tibble(
  folder = '/Volumes/vandenBrinkLab/deep_sequencing'
)

upenn2_files <- upenn2 %>% 
  pull(folder) %>% 
  map_dfr(function(f){
    upenn %>% 
      set_names(upenn) %>% 
      imap_dfr( ~ Sys.glob(str_glue('{f}/{..1}/*/*')) %>% 
             data_frame %>% 
              mutate(..2)) %>% 
      rename(directory = names(.)[1],
             projectID = names(.)[2])
  }) %>% 
  mutate(sample_folder = str_extract(directory, 'Sample_.+$'),
         fid = str_replace(sample_folder, 'Sample_',''),
         fid = str_replace(fid, '_IGO_.+$','')) %>% 
  mutate(pid = str_replace(fid, 'MS_UPENN_','')) %>% 
  mutate(pid = str_pad(pid, 2, side = 'left', pad = '0'))

# the pheno of the ptb from John
upenn <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/U Penn/patients/upenn_essential_data_v3.xlsx', sheet = 2) %>% 
  filter(!is.na(pt_id)) %>% 
  mutate(pt_id = as.character(pt_id)) %>% 
  mutate(pid = str_replace(pt_id, '^80',''))

upenn_samp <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/U Penn/samples/sample_mapping_UPenn.xlsx') %>% 
  select(pt_id, OligoID) %>% 
  mutate(pt_id = as.character(pt_id))

upenn_all <- upenn2_files %>% 
  left_join(upenn) %>% 
  full_join(upenn_samp)

upenn_all %>% 
  write_csv('../data/shotgun_pheno/upenn_all_earlier.csv')

upenn_up <- upenn_all %>% 
  select(directory, projectID, OligoID, fid) %>% 
  rename(sampleid = OligoID)
```

```{r}
# 11-24 to be uploaded 
nov24_up <- bind_rows(upenn_up, italy_up)

nov24_up %>% 
  write_csv('/Volumes/vandenbrinklab/Angel_Dai/Full_human_shotgun_catalog/shotgun_cart_earlier.csv')
```

@@

sometimes it doesn't work you just need to restart R and run it again

```{r}
# change the d_set_input in the upload_data_from_query_OTU_AD.R script 
source('../../../microbiome_db/SQL/scripts/upload_data_from_query_OTU_AD.R')
upload_data_from_query_OTU(1) # changed the file path of the table getting uploaded 
```
